\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-09 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
improved two comments

IMPORTANT: it is your responsibility to make sure that in the input CUBIT (or similar) mesh
that this code will read in SPECFEM3D format from files "nodes\_coords\_file" and "mesh\_file"
you have created layers of elements that constitute a layer of constant thickness aligned
with the coordinate grid axes (X, Y and/or Z), so that this code can assign CPML flags to them.
This code does NOT check that (because it cannot, in any easy way).
The mesh inside these CPML layers does not need to be structured nor regular, any non-structured
mesh is fine as long as it has flat PML inner and outer faces, parallel to the axes, and thus
of a constant thickness.
The thickness can be different between the X, Y and Z sides. But for X it must not vary,
for Y it must not vary, and for Z it must not vary.
If you do not know the exact thickness, or if you think the thickness may have tiny variations,
for instance due to roundoff issues when exporting the mesh, you can use a slightly LARGER value
in this code (say 2\% to 5\% more), and this code will fix that and will adjust it; never use
a SMALLER value otherwise this code will miss some CPML elements.

@@

\item [nummaterial\_velocity\_file] Defines the material properties.
\begin{itemize}
\item For classical materials (i.e., spectral elements for which the velocity and density
model will not be assigned by calling an external function to define for instance a tomographic model), the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}  \texttt{Q}  \texttt{anisotropy\_flag}
\end{lyxcode}
where \texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a unique identifier,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag} an identifier for anisotropic models.
%%magnoni
\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the} and Section \ref{sec:Using-tomographic} `Using external tomographic Earth models' for further details.
%
\end{itemize}

>>>>

IMPORTANT: it is your responsibility to make sure that in the input CUBIT (or similar) mesh
that this code will read in SPECFEM3D format from files "nodes\_coords\_file" and "mesh\_file"
you have created layers of elements that constitute a layer of constant thickness aligned
with the coordinate grid axes (X, Y and/or Z), so that this code can assign CPML flags to them.
This code does NOT check that (because it cannot, in any easy way).
The mesh inside these CPML layers does not need to be structured nor regular, any non-structured
mesh is fine as long as it has flat PML inner and outer faces, parallel to the axes, and thus
of a constant thickness.
The thickness can be different for the X, Y and Z sides. But for X it must not vary,
for Y it must not vary, and for Z it must not vary.
If you do not know the exact thickness,
you can use a slightly LARGER value
in this code (say 2\% to 5\% more) and this code will fix that and will adjust it; never use
a SMALLER value otherwise this code will miss some CPML elements.

@@

\item [nummaterial\_velocity\_file] Defines the material properties.
\begin{itemize}
\item For classical materials (i.e., spectral elements for which the velocity and density
model will not be assigned by calling an external function to define for instance a tomographic model), the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}  \texttt{Q}  \texttt{anisotropy\_flag}
\end{lyxcode}
where \textbf{\texttt{domain\_ID} is 1 for acoustic and 2 for elastic or viscoelastic materials,}
\texttt{material\_ID} a unique identifier,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag} an identifier for anisotropic models.
%%magnoni
\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the} and Section \ref{sec:Using-tomographic} `Using external tomographic Earth models' for further details.
%
\end{itemize}
